Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness: An Analysis of the General Social Survey (GSS) Data from 1972 to 2012

### 2023-03-28 outputs/paper/paper.qmd
Add files via upload

---
title: "Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness: An Analysis of the General Social Survey (GSS) Data from 1972 to 2012"
subtitle: ""
author: 
  - SHAOHAN CHANG
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper presents an analysis of a subset of the General Social Survey (GSS) data from the year 1972, which includes information on individuals' demographic characteristics, health, finances, living arrangements, and subjective well-being. The study aimed to explore various aspects of individuals' lives during the early 1970s in the United States, such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.The dataset consists of 5 observations and 10 variables, including year, age, sex, babies, divorce, health, finance_satisfied, living_area, and happy. The study used graphical representation to analyze the relationships between different variables in the dataset and individuals' level of happiness. The results of the analysis suggest that there is a positive relationship between people's satisfaction with their current financial situation, their self-rated health, and their level of happiness in life. Additionally, being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling not too happy. Moreover, the study found that people's level of education is positively associated with their level of happiness in life, as people's education level increases, their level of happiness also gradually increases.Overall, this study provides valuable insights into various aspects of individuals' lives during the early 1970s in the United States. The findings can be useful for researchers and students interested in exploring topics such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being. The study highlights the importance of considering different factors that can influence individuals' level of happiness and well-being, such as their financial situation, health status, and level of education. Further research could investigate more recent data from the GSS to examine changes in these relationships over time."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Exploring Relationships between Demographic Characteristics, Health, Finances, Living Arrangements, and Happiness: An Analysis of the General Social Survey (GSS) Data from 1972 to 2012"
subtitle: ""
author: 
  - SHAOHAN CHANG
thanks: "Code and data are available at: https://github.com/lucas11333/Factor_of_Wellbeing"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper presents an analysis of a subset of the General Social Survey (GSS) data from the year 1972, which includes information on individuals' demographic characteristics, health, finances, living arrangements, and subjective well-being. The study aimed to explore various aspects of individuals' lives during the early 1970s in the United States, such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being.The dataset consists of 5 observations and 10 variables, including year, age, sex, babies, divorce, health, finance_satisfied, living_area, and happy. The study used graphical representation to analyze the relationships between different variables in the dataset and individuals' level of happiness. The results of the analysis suggest that there is a positive relationship between people's satisfaction with their current financial situation, their self-rated health, and their level of happiness in life. Additionally, being divorced may have a slight impact on one's level of happiness in life, with a small proportion of individuals feeling not too happy. Moreover, the study found that people's level of education is positively associated with their level of happiness in life, as people's education level increases, their level of happiness also gradually increases.Overall, this study provides valuable insights into various aspects of individuals' lives during the early 1970s in the United States. The findings can be useful for researchers and students interested in exploring topics such as social stratification, gender roles, family dynamics, health disparities, and subjective well-being. The study highlights the importance of considering different factors that can influence individuals' level of happiness and well-being, such as their financial situation, health status, and level of education. Further research could investigate more recent data from the GSS to examine changes in these relationships over time."
format: pdf
number-sections: true
bibliography: references.bib
---
